---
title: "Variable Names"
author: "Nicholas Kondo, "
subtitle: 
output:
  html_document:
    df_print: paged
  html_notebook: default
---

```{r setup, include=FALSE}

# Please leave this code chunk as is. It makes some slight formatting changes to alter the output to be more aesthetically pleasing. 

library(knitr)

# Change the number in set seed to your own favorite number
set.seed(4)
options(width=70)
options(scipen=99)


# this sets text outputted in code chunks to small
opts_chunk$set(tidy.opts=list(width.wrap=50),tidy=TRUE, size = "vsmall")  
opts_chunk$set(message = FALSE,                                          
               warning = FALSE,
               # "caching" stores objects in code chunks and only rewrites if you change things
               cache = TRUE,                               
               # automatically downloads dependency files
               autodep = TRUE,
               # 
               cache.comments = FALSE,
               # 
               collapse = TRUE,
               # change fig.width and fig.height to change the code height and width by default
               fig.width = 5.5,  
               fig.height = 4.5,
               fig.align='center')


```

```{r setup-2, include=FALSE}

# Always print this out before your assignment
sessionInfo()
getwd()

```


<!-- ### start answering your problem set here -->
<!-- You may export your homework in either html or pdf, with the former usually being easier. 
     To export or compile your Rmd file: click above on 'Knit' then 'Knit to HTML' -->
<!-- Be sure to submit both your .Rmd file and the compiled .html or .pdf file for full credit -->


```{r setup-3, include=FALSE}
# loading all libraries
library(tidyverse)
library(dplyr)
library(tidyr)
library(worldfootballR)
library(dplyr)
library(tidyverse)
library(worldfootballR)
library(utils)
library(rsample)
library(glmnet)
library(glmnetUtils)
library(forcats)
library(rsample)
library(ggplot2)
library(sjPlot)

# note, do not run install.packages() inside a code chunk. install them in the console outside of a code chunk. 
```

# Introduction 

For this study, data was collected from FBref.com on the "Big 5" Leagues.  Our data includes statistics in categories such as standard, shooting, passing, goal and shot creation, defense, miscellaneous, playing time, and market values.  We compare a player's statistics with their market values listed on TransfrMarket.com and find the statistics that are most correlated with a player's market values.  In other words, we are aiming to find the certain statistics that makes a player valuable.  

```{r,include=FALSE}

#Loading the data sets 

standard <- fb_big5_advanced_season_stats(season_end_year = c(2018:2020), stat_type = "standard", team_or_player = "player")

shooting <- fb_big5_advanced_season_stats(season_end_year = c(2018:2020), stat_type = "shooting", team_or_player = "player")

passing <- fb_big5_advanced_season_stats(season_end_year = c(2018:2020), stat_type = "passing", team_or_player = "player")

passingtypes <- fb_big5_advanced_season_stats(season_end_year = c(2018:2020), stat_type = "passing_types", team_or_player = "player")

gca <- fb_big5_advanced_season_stats(season_end_year = c(2018:2020), stat_type = "gca", team_or_player = "player")
```

```{r, include=FALSE}
defense <- fb_big5_advanced_season_stats(season_end_year = c(2018:2020), stat_type = "defense", team_or_player = "player")
possession <- fb_big5_advanced_season_stats(season_end_year = c(2018:2020), stat_type = "possession", team_or_player = "player")
misc <- fb_big5_advanced_season_stats(season_end_year = c(2018:2020), stat_type = "misc", team_or_player = "player")
playingtime <- fb_big5_advanced_season_stats(season_end_year = c(2018:2020), stat_type = "playing_time", team_or_player = "player")
keepers <- fb_big5_advanced_season_stats(season_end_year = c(2018:2020), stat_type = "keepers", team_or_player = "player")
keepers_adv <- fb_big5_advanced_season_stats(season_end_year = c(2018:2020), stat_type = "keepers_adv", team_or_player = "player")
```

Retrieving the market values
```{r, include=FALSE}
# Loading the market values

market_values17 <- get_player_market_values(country_name = c("England", "Spain", "France", "Italy", "Germany"), start_year = 2017)
```


```{r, include=FALSE}

# Renaming the variables

standard <- standard %>% 
  rename(Matches_PLayed = MP_Playing,
         Starts = Starts_Playing,
         Min = Min_Playing,
         Min_per_90 = Mins_Per_90_Playing,
         xG = xG_Expected,
         npxG = npxG_Expected,
         xA = xA_Expected,
         'npxG+xA' = 'npxG+xA_Expected')
    
shooting <- shooting %>% 
  rename(Gls = Gls_Standard,
         Sh = Sh_Standard,
         SoT = SoT_Standard,
         SoT_percent = SoT_percent_Standard,
         SoT_per_90 = SoT_per_90_Standard,
         Sh_per_90_Standard = Sh_per_90_Standard,
         SoT_per_90 = SoT_per_90_Standard,
         G_per_Sh = G_per_Sh_Standard,
         G_per_SoT = G_per_SoT_Standard,
         Dist = Dist_Standard,
         FK = FK_Standard,
         PK = PK_Standard,
         PKatt = PKatt_Standard,
         xG = xG_Expected,
         npxG = npxG_Expected,
         npxG_per_Sh = npxG_per_Sh_Expected,
         G_minus_xG = G_minus_xG_Expected,
         npG_minus_xG = 'np:G_minus_xG_Expected')

defense <- defense %>% 
  rename(
Tkl = Tkl_Tackles,
TklW = TklW_Tackles,
Def_3rd = 'Def 3rd_Tackles',
Mid_3rd = 'Mid 3rd_Tackles',
Att_3rd = 'Att 3rd_Tackles',
Tkl_vs_dribble = Tkl_Vs,
Att_vs_dribble = Att_Vs,
Successful_Pressure_Percent = Tkl_percent_Vs,
Def_3rd_Pressures = 'Def 3rd_Pressures',
Mid_3rd_Pressures = 'Mid 3rd_Pressures',
Att_3rd_Pressures = 'Att 3rd_Pressures',
Blocks = Blocks_Blocks)

possession <- possession %>% 
  rename(
    Touches = Touches_Touches,
    Def_3rd_Touches = 'Def 3rd_Touches',
    Mid_3rd_Touches = 'Mid 3rd_Touches',
    Att_3rd_Touches = 'Att 3rd_Touches',
    Att_Pen_Touches = 'Att Pen_Touches',
    Carries = Carries_Carries)
```


# Appendix 

## Standard

`Season_End_Year`: The year at the end of the season.

`Squad`: The team the player plays on.

`Player`: The name of the player.

`Nation`: Nationality of the Player.

`Pos`: The player's position

`Age`: Current Age

`Born`: Year of Birth

`Matches_Played`:

`Starts`: Games Started

`Min`: Minutes Played

`Min_per_90`: Minutes Played divided by 90 

`Gls`: Goals 

`Ast`: Assists

`G_minus_PK`: Goals minus Penalty Kicks

`PK`: Penalty Kicks Made

`PKatt`: Penalty Kicks Attempted

`CrdY`: Yellow cards

`CrdR`: Red Cards

`Gls_Per`: Goals Scored per 90 minutes

`Ast_Per`: Assists per 90 minutes

`G+A_Per`: Goals and Assists per 90 minutes 

`G_minus_PK_Per`: Goals minus Penalty Kicks per 90 minutes 

`G+A_minus_PK_Per`: Goals and Assists minus Penalty Kicks per 90 minutes 

`xG`: Expected Goals

`npxG`: Non-Penalty Expected Goals

`xA`: xG Assisted

`npxG+xA`: Non Penalty Expected Goals plus xG Assisted

`xG_Per`: Expected Goals per 90 minutes

`xA_Per`: xG Assisted per 90 minutes

`xG+xA_Per`: Expected Goals plus Assist per 90 minutes

`npxG_Per`: Non-Penalty Expected Goals per 90 minutes

`npxG+xA_Per`: Non-Penalty Expected Goals plus xG Assisted per 90 minutes

## Goalkeeping - Luke 

### Advanced Goalkeeping - Luke

## Shooting - Darron

`Season_End_Year`: The year at the end of the season.

`Squad`: The team the player plays on.

`Player`: The name of the player.

`Nation`: Nationality of the Player.

`Pos`: The player's position

`Age`: Current Age

`Born`: Year of Birth

`Mins_per_90`: Minutes played divided by 90

`Gls`: Goals scored or allowed

`SH`: Shots Total

`SoT`: Shots on target

`SoT_percent`: Shots on target percentage
Percentage of shots that are on target

`Sh_per_90`: Shots total per 90 minutes

`Sot_per_90`: Shots on target per 90 minutes

`G_per_Sh`: Goals per shot

`G_per_SoT`: Goals per shot on target

`Dist`: Average distance, in yards, from goal of all shots taken

`FK`: Shots from free kicks

`PK`: Penalty Kicks Made

`PKatt`: Penalty Kicks Attempted

`xG`: Expected Goals

`npxG`: Non-Penalty Expected Goals

`npxG_per_Sh`: Non-Penalty Expected Goals per shot

`G_minus_xG`: Goals minus Expected Goals

`npG_minus_npxG`: Non-Penalty Goals minus Non-Penalty Expected Goals

## Passing - Luke 

## Pass Types - Luke 

## Goal and Shot Creation - Luke 

## Defensive Actions - Darron

`Season_End_Year`: The year at the end of the season.

`Squad`: Team

`Comp`: Completions

`Player`: Players name

`Nation`: Players Nationality

`Pos`: Players position

`Age`: Current age

`Born`: Year of Birth

`Mins_Per_90`: Minutes played divided by 90
 
`Tkl`: Number of players tackled

`TklW`: Tackles in which the tackler's team won possession of the ball

`Def_3rd`: Tackles in defensive 1/3

`Mid_3rd`: Tackles in middle 1/3

`Att_3rd`: Tackles in attacking 1/3

`Tkl_vs_dribble`: Number of dribblers tackled

`Att_vs_dribble`: Number of times dribbled past plus number of tackles

`Press_Pressures`: Number of times applying pressure to opposing player who is receiving, carrying or releasing the ball

`Succ_Pressures`: Number of times the squad gained possession withing five seconds of applying pressure

`Successful_Pressure_Percent`: Percentage of time the squad gained possession withing five seconds of applying pressure

`Def_3rd_Pressures`: Number of times applying pressure to opposing player who is receiving, carrying or releasing the ball, in the defensive 1/3

`Mid_3rd_Pressures`:Number of times applying pressure to opposing player who is receiving, carrying or releasing the ball, in the middle 1/3

`Att_3rd_Pressures`: Number of times applying pressure to opposing player who is receiving, carrying or releasing the ball, in the attacking 1/3

`Blocks`: Number of times blocking the ball by standing in its path

`Sh_Blocks`: Number of times blocking a shot by standing in its path

`ShSv_Blocks`: Number of times blocking a shot that was on target, by standing in its path

`Pass_Blocks`: Number of times blocking a pass by standing in its path

`Int`: Interceptions

`Tkl+Int`: Number of players tackled plus number of interceptions

`Clr`: Clearances

`Err`: Mistakes leading to an opponent's shot

## Possessions - Darron 

`Season_End_Year`:

`Squad`:

`Comp`:

`Player`:

`Nation`:

`Pos`: Possession

`Age`:

`Born`:

`Touches`: Number of times a player touched the ball

`Def_Pen`: Touches in defensive penalty area

`Def_3rd_Touches`: Touches in defensive 1/3

`Mid_3rd_Touches`: Touches in middle 1/3

`Att_3rd_Touches`: Touches in attacking 1/3

`Att_Pen_Touches`: Touches in attacking penalty area

`Live_Touches`: Live-ball touches

`Succ_Dribbles`: Dribbles Completed Successfully

`Att_Dribbles : Dribbles Attempted

`Succ_percent_Dribbles`: Percentage of Dribbles Completed Successfully

`#Pl_Dribbles`: Number of Players Dribbled Past

`Megs_Dribbles`: Number of times a player dribbled the ball through an opposing player's legs

`Carries`: Number of times the player controlled the ball with their feet

`TotDist_Carries`: Total distance, in yards, a player moved the ball while controlling it with their feet, in any direction

`PrgDist_Carries`: Progressive Distance; Total distance, in yards, a player moved the ball while controlling it with their feet towards the opponent's goal

`Prog_Carries`: Carries that move the ball towards the opponent's goal at least 5 yards, or any carry into the penalty area

`Final_Third_Carries`: Carries that enter the 1/3 of the pitch closest to the goa

`CPA_Carries`: Carries into the 18-yard box

`Mis_Carries`: Number of times a player failed when attempting to gain control of a ball

`Dis_Carries`: Number of times a player loses control of the ball after being tackled by an opposing player

`Targ_Receiving`: Number of times a player was the target of an attempted pass

`Rec_Receiving`: Number of times a player successfully received a pass

`Rec_percent_Receiving`: Passes Received Percentage

`Prog_Receiving`: Progressive Passes Received


## Playing Time - Nick 

`Season_End_Year`:

`Squad`:

`Comp`:

`Player`:

`Nation`:

`Pos`:

`Age`:

`Born`:

`MP`:

`Min`:

`Min_per_MP`:

`Min_percent_Playing.Time`:
Mins_per_90
Starts
Mn_per_Start



`Mins_per_90`:

`Starts`:

`Mn_per_Start`:

`Compl`:

`Subs`:

`Mn_per_Sub`:

`Mn_per_Sub`:

`unSub`:

`PPM`:

`onG`:

`onGA`:

`plus_per_minus`:

`plus_per_minus_per_90`:

`On_minus_Off`:

`onxG`:

`onxGA`:

`xGplus_per_minus`:

`xGplus_per_minus_per_90`:

`xGplus_per_minus_per_90:`

# Misc - Nick 

# Market Values Table - Nick 


